An Embedding Framework for Consistent Polyhedral Surrogates

### 2019-07-16 neurips-19/poly-embed.tex
Making notation consistent.
Fixing a typo

\begin{figure}
	\begin{minipage}{0.42\linewidth}
		\centering
		\includegraphics[width=\linewidth]{tikz/original-top-k}
		\label{fig:original-top-k}
	\end{minipage}
	\hfill
	\begin{minipage}{0.42\linewidth}
		\centering
		\includegraphics[width=\linewidth]{tikz/finite-surrogate-top-k}
		\label{fig:finite-surrogate-top-k}
	\end{minipage}
	\caption{Minimizers of $\elltop{2}$ and $\L^2$, respectively, as a function of $p$.}
	\label{fig:top-k-simplices}
\end{figure}

Figure~\ref{fig:top-k-simplices} (left) gives a map of the property values of $\gamma^{\text{top-2}} := \prop{\elltop{2}}$ over $\Delta_3$.
Similarly, for every distribution $p \in \Delta_3$, $\inprod{p}{L^2}$ has a minimizer in the set $\R'$ composed of the tuples shown in Figure~\ref{fig:top-k-simplices} (right), and thus $\risk{L^2} = \risk{\ell^2}$, where $\ell^2 := L^2|_{\R'}$.
%Therefore, we know $L^2$ embeds $\ell^2$ by Proposition~\ref{prop:embed-bayes-risks}.
%(Each cell in this simplex is a level set $\gamma^{\text{top-2}}_r$ and corresponds to a flat piece of the Bayes Risk $\risk{\elltop{2}}$.)

By visual inspection, we can observe there is no ``refining'' mapping from $\gamma^{\text{top-2}}$ to $\gamma^2 := \prop{\ell^2}$.
By refining, we loosely mean that, for some $j \in \R$, there is no $I \subseteq \reals^n$ such that $\cup_{i \in I}\gamma^2_i = \gamma^{\text{top-2}}_{j}$.
%If such a mapping existed, it would allude to one possible consistent link $\psi$ by which $L^2$ embeds $\elltop{2}$.
Conversely, we can ``refine'' $\prop{L^2}$ down to $\prop{\ell^2}$ by using the axiom of choice to construct $\R'$.

>>>>

\begin{figure}
	\begin{minipage}{0.42\linewidth}
		\centering
		\includegraphics[width=\linewidth]{tikz/original-top-k}
		\label{fig:original-top-k}
	\end{minipage}
	\hfill
	\begin{minipage}{0.42\linewidth}
		\centering
		\includegraphics[width=\linewidth]{tikz/finite-surrogate-top-k}
		\label{fig:finite-surrogate-top-k}
	\end{minipage}
	\caption{Minimizers of $\inprod{p}{\elltop{2}}$ and $\inprod{p}{\ell^2}$, respectively, varying $p$ over $\Delta_3$.}
	\label{fig:top-k-simplices}
\end{figure}

Figure~\ref{fig:top-k-simplices} (left) gives a map of the property values of $\gamma^{\text{top-2}} := \prop{\elltop{2}}$ over $\Delta_3$.
Similarly, for every distribution $p \in \Delta_3$, $\inprod{p}{L^2}$ has a minimizer in the set $\R'$ composed of the tuples shown in Figure~\ref{fig:top-k-simplices} (right), and thus $\risk{L^2} = \risk{\ell^2}$, where $\ell^2 := L^2|_{\R'}$, so Figure~\ref{fig:top-k-simplices} (right) shows $\gamma^2 := \prop{\ell^2}$.
%Therefore, we know $L^2$ embeds $\ell^2$ by Proposition~\ref{prop:embed-bayes-risks}.
%(Each cell in this simplex is a level set $\gamma^{\text{top-2}}_r$ and corresponds to a flat piece of the Bayes Risk $\risk{\elltop{2}}$.)

By visual inspection, we can observe there is no ``refining'' mapping from $\gamma^{\text{top-2}}$ to $\gamma^2$.
In refining, we loosely mean that, for some $j \in \R$, there is no $I \subseteq \reals^n$ such that $\cup_{i \in I}\gamma^2_i = \gamma^{\text{top-2}}_{j}$.
%If such a mapping existed, it would allude to one possible consistent link $\psi$ by which $L^2$ embeds $\elltop{2}$.
Conversely, we can ``refine'' $\prop{L^2}$ down to $\prop{\ell^2}$ by using the axiom of choice to construct $\R'$.
